\documentclass{beamer}

\title{\large Solution of Optimization Problems in Mathcad Prime\textsuperscript{\tiny\textregistered}}
\author{Fərid Fərəcli \and Orxan Məmmədli \and Tayfur Tağıyev}
\institute{Azerbaijan State Oil and Industry University}

\usetheme{Frankfurt}
\usepackage{fontspec}

\begin{document}

\maketitle

\begin{frame}
\frametitle{Table of Contents}
\tableofcontents
\end{frame}

\section{Introduction}

\begin{frame}{What is Optimization}
\begin{itemize}
\item Optimization is the process of finding the best possible solution from a set of feasible solutions.
\vspace{10pt}
\item It involves maximizing or minimizing an objective function (e.g., cost, time, efficiency).
\vspace{10pt}
\item Common in engineering, economics, logistics, design, etc.
\end{itemize}
\end{frame}

\begin{frame}{Types of Optimization Problems}
\begin{itemize}
\item Linear vs. Nonlinear
\item Unconstrained vs. Constrained
\item Single-objective vs. Multi-objective
\item Continuous vs. Discrete (Integer Optimization)
\end{itemize}
\end{frame}

\begin{frame}{What is Mathcad Prime\textsuperscript{\tiny\textregistered}}
\begin{itemize}
\item Mathcad Prime\textsuperscript{\tiny\textregistered} is a technical computing software developed by PTC.
\vspace{10pt}
\item Designed for engineering calculations, documentation, and mathematical analysis.
\vspace{10pt}
\item Combines live math, units handling, and text formatting in a single worksheet.
\end{itemize}
\end{frame}

\begin{frame}{}
\begin{center}
Thank you for attention!
\end{center}
\end{frame}

\end{document}
